Maximum Allowable Current Determination of Arbitrary Reconfigurable Battery Systems By Using a Directed Graph Model Combined with Greedy Algorithm

### 2023-06-26 paper/main.tex
修改了 SP 部分

% 0623 v3.0 plan 具体修改计划
% !!!!!! 先改方法、后改案例、最后改介绍和其他
% -[ ] 题目 点明我们的普适性、自动化？
% -[ ] 摘要 中间段重写；点明普适性、自动化
% -[ ] introduction 
%      -[ ] 不放案例；
%      -[ ] 增加重构灵活性的文献；
%      -[ ] 有向图的文献；
%      -[ ] 点明普适性、自动化
% -[ ] methodology 
%      -[x] main 图重画，只保留文字；
%      -[x] 有向图模型，说清三层关系，更规矩地写建模过程；
%      -[ ] 优化目标和约束；
%      -[ ] 最短路径，逐句逐字去捋顺；
%      -[ ] 贪心算法，结合流程图说明算法过程，把二分法融进去；
%      -[ ] 增加隔离的处理，如约束、算法的改动
% -[ ] case study 
%      -[ ] 考虑新结构（MAC=4，想不到就算了，仍用ef结构）；
%      -[ ] results 直接给出结果，略去计算细节；
%      -[ ] discussion 说明eta的合理性；
%      -[ ] 什么样的结构能获得更大的MAC（易隔离性和输出性能的冲突）（想不出来就算了）；
%      -[ ] 电池隔离场景下的MAC变化(比较不同结构)

@@

However, it is computationally difficult to solve \ref{eq:max_eta} because of the $\bm{Y}_n^{-1}$.
On one hand, due to the introduction of nonlinear terms by $\bm{Y}_n^{-1}$, many effective methods in linear optimization are not suitable for this problem.
On the other hand, the rank of $Y_{n}$ is proportional to the number of batteries and switches, which can be very large for a large RBS system, leading to significant computational burden.
Therefore, intelligent algorithms that rely on evolving by iteration may face efficiency issues when dealing with large RBS system.
In order to address this issue, the problem should be considered from the perspective of guiding the RBS to reconstruct as many parallel structures as possible.
Consequently, a greedy algorithm based on the shortest path is proposed. 
The detailed implementation process is presented in the following two subsections.

@@

\subsection{Shortest Path}
% 计算SP的部分单独一个 subsection
% 添点内容，修改下面两句话
A path is defined by the complete route passing through one battery (or a consecutive series of batteries) and closed switches from the anode $v_1$ to cathode $v_N$ of the RBS.
Assuming a situation that battery $i$ is connected to the anode $v_1$ and the cathode $v_N$ of the RBS by a path $p$ in the graph model.
Then the distance $\omega$ of the path $p$ is defined by the following equation: % 给出使用 Ns的原因，在这句开头，利用RBS的灵活性，通过额外的开关实现一条path上的电池数尽可能少，因此对路径p上的电池数量进行惩罚，设其权重为Ns，而路径p上的开关数量的权重设为1，从而使得最短路径表示的是电池数量最少的情况。 #TODO: 好好想这句话怎么写清楚
\begin{equation}\label{eq:weight}
    \omega(p) = N_s \cdot n_b (p) + n_s (p),
\end{equation}
where $N_s$ is the total number of switches in the system; $n_b(p)$ and $n_s(p)$ are number of batteries and switches in the path $p$ respectively. 
$SP_i$ is defined as the path with the minimum $\omega$ for battery $i$.
\begin{equation}\label{eq:def_sp}
    SP_i = \mathop{\arg\min}_{p \in P_i} \omega(p),
\end{equation}
where $P_i$ is the set of all paths from $v_1$ to $v_N$ which pass through the directed edge $i$.
The Dijkstra algorithm can be used to implement the $SP_i$. % 简短说下过程，给参考文献

% SP 的控制角度意义
% 在下一章节详细说明，如何利用SP求解MAC
% SP 的作用，好好解释，下段重写(是不是该挪到下一subsection)
According to the definition, $SP_i$ gives the simplest strategy by which the control of battery $i$ is achieved with a minimum of switches while minimizing the influence of other batteries.
From the perspective of series/parallel, the more batteries are connected into circuit via their $SP$s, the more batteries are connected in parallel.

@@

>>>>

% 0623 v3.0 plan 具体修改计划
% !!!!!! 先改方法、后改案例、最后改介绍和其他
% -[ ] 题目 点明我们的普适性、自动化？
% -[ ] 摘要 中间段重写；点明普适性、自动化
% -[ ] introduction 
%      -[ ] 不放案例；
%      -[ ] 增加重构灵活性的文献；
%      -[ ] 有向图的文献；
%      -[ ] 点明普适性、自动化
% -[ ] methodology 
%      -[x] main 图重画，只保留文字；
%      -[x] 有向图模型，说清三层关系，更规矩地写建模过程；
%      -[x] 优化目标和约束；
%      -[ ] 最短路径，逐句逐字去捋顺；
%      -[ ] 贪心算法，结合流程图说明算法过程，把二分法融进去；
%      -[ ] 增加隔离的处理，如约束、算法的改动
% -[ ] case study 
%      -[ ] 考虑新结构（MAC=4，想不到就算了，仍用ef结构）；
%      -[ ] results 直接给出结果，略去计算细节；
%      -[ ] discussion 说明eta的合理性；
%      -[ ] 什么样的结构能获得更大的MAC（易隔离性和输出性能的冲突）（想不出来就算了）；
%      -[ ] 电池隔离场景下的MAC变化(比较不同结构)

@@

However, it is computationally difficult to solve \ref{eq:max_eta} because of the $\bm{Y}_n^{-1}$.
On one hand, due to the introduction of nonlinear terms by $\bm{Y}_n^{-1}$, many effective methods in linear optimization are not suitable for this problem.
On the other hand, the rank of $Y_{n}$ is proportional to the number of batteries and switches, which can be very large for a large RBS system, leading to significant computational burden.
Therefore, intelligent algorithms that rely on evolving by iteration may face efficiency issues when dealing with large RBS system.
% 如果有时间，可以在案例部分做个对比，看看智能算法和本文算法的效率差距有多大。
In order to address this issue, the problem should be considered from the perspective of guiding the RBS to reconstruct as many parallel structures as possible.
Consequently, a greedy algorithm based on the shortest path is proposed. 
The detailed implementation process is presented in the following two subsections.

@@

\subsection{Shortest Path}

The path $p$ used in this method is defined as the complete route that passes through one battery (or a consecutive series of batteries) and closed switches, connecting the anode $v_1$ to the cathode $v_N$ of the RBS.
By applying a penalty to the series-connected batteries on the path, where additional batteries imply a longer distance, the algorithm encourages the RBS to form parallel structures as much as possible.
Meanwhile, to reduce the number of switches controlled during the reconstruction process, a penalty is also applied to the total number of switches on the path, while ensuring the minimum number of batteries.
Therefore, the distance $\omega$ of the path $p$ is defined by the following equation: 
\begin{equation}\label{eq:weight}
    \omega(p) = N_s \cdot n_b (p) + n_s (p),
\end{equation}
where $N_s$ is the total number of switches in the system; 
$n_b(p)$ and $n_s(p)$ are number of batteries and switches in the path $p$ respectively. 
Moreover, the shortest path $SP_i$ is defined as the path with the minimum $\omega$ for battery $i$, as shown in the following equation:
\begin{equation}\label{eq:def_sp}
    SP_i = \mathop{\arg\min}_{p \in P_i} \omega(p),
\end{equation}
where $P_i$ is the set of all paths from $v_1$ to $v_N$ which pass through the directed edge $i$.

The $SP_i$ can be solved by the Dijkstra algorithm.
The Dijkstra algorithm is a graph search method that finds the shortest path between two given nodes in a weighted graph, efficiently solving the single-source shortest path problem.
Assuming that the cathode and anode of battery $i$ are denoted as $v_i^-$ and $v_i^+$ respectively, the path $p$ of battery $i$  can be divided into three segments : $v_1 \rightarrow v_i^-$, $v_i^+ \rightarrow v_N$, and $v_i^- \rightarrow v_i^+$.
The $v_i^- \rightarrow v_i^+$ is the directed edge corresponding to battery $i$. 
With the Dijkstra algorithm, shortest paths for the $v_1 \rightarrow v_i^-$ and $v_i^+ \rightarrow v_N$ can be calculated under the weights given in Eq. \ref{eq:weight}, denoted as $SP(v_i^- \rightarrow v_i^+)$ and $SP(v_i^+ \rightarrow v_N)$, respectively.
Finally, the $SP_i$ for battery $i$ is formed by the complete path with $SP(v_1 \rightarrow v_i^-)$, $v_i^- \rightarrow v_i^+$, and $SP(v_i^+ \rightarrow v_N)$.

@@

From the perspective of series/parallel, the more batteries are connected into circuit via their $SP$s, the more batteries are connected in parallel.
